### 2014-05-08 paper.tex
updated paper.tex

\documentclass[10pt, letterpaper]{article}

\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}

%%%%%%%%%%%%%%%%%%%%%%% Title info %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{Kiran Vodrahalli, Evelyn Ding, Albert Lee}
\title{Word Sense Disambiguation: Pipelining with Supervised LSA}
\date{May 8, 2014}

\begin{document}

	\maketitle

	\section{Introduction}
	\section{Previous Work}
	\section{Data}
	\section{Algorithms}
	\section{Results}
	\section{Conclusions}
	\section{Future Work}

\end{document}

### 2014-05-08 paper.tex
compiled latex
partially finished copying slides to paper -- need furhter elaboration obviously, and need to finish copying slides to paper

@@
 	\section{Introduction}
+	\subsection{Problem Statement}
+	  Multiple word senses
+
+	  ex. bank: "financial institution" or "river bank" or "count on something happening" or "supply/stock held in supply for future use" ...
+
+	  Wrong sense can drastically alter meaning
+
+	  Objective: given context, determine which sense of the word is intended
+
+	  First proposed by Weaver in 1949 as computational task in the early days of MT
+
+	  One of the oldest open problems in computational linguistics
+
+	  AI-Complete Problem
+
+	  Example
+
+	  "Paintings, drawings and sculpture from every period of art during the last 350 years will be on display ranging from a Tudor portrait to contemporary British art."
+	  vs.
+	  "Through casual meetings at cafe's, the artists drew together to form a movement in protest against the waste of war, against nationalism and against everything pompous, conventional or boring in the art of the Western world."
+
+	  the creation of beautiful or significant things 
+      vs. 
+	  the products of human creativity; works of art collectively 
 	\section{Previous Work}
+	knowledge based
+
+	unsupervised corpus-based
+
+	supervised corpus-based
+	\subsection{Knowledge-based}
+	Lesk's algorithm:
+two words W1 and W2 with multiple word senses
+for each sense i in W1
+for each sense j in W2
+calculate overlap of i and j in dictionary definitions
+maximize overlap i and j to determine word senses
+Semantic similarity:
+calculate path between words in wordnet for each word sense with other words in the context
+minimize total semantic path to select word sense
+context can vary from one sentence to length of document
+
+	\subsection{Unsupervised Corpus-based}
+	 Token-based discrimination: cluster contexts in which a given target word appears
+	 Cluster 1: The line was occupied. 
+	 The operator came into the line abruptly.
+
+	 Cluster 2: The line was really long and it took forever to be served. 
+ 	 I stood in the queue for about 10 minutes
+
+ 	 Use parallel corpus across language to infer sense distinctions across the language
+	 Je vais prendre ma propre décision.
+	 vs.
+	 Je vais prendre ma propre voiture.
+	\subsection{Supervised Corpus-based}
+	 Use annotated corpus to build model
+ 	 ex. to know: 1) be aware of piece of information
+                              I want to know who is winning.
+                              I know that the president lied.
+                             2) know person
+                             She doesn't know the composer.
+                             Do you know my sister?
+	 Use context of how word usually appears (bigram/trigram models)
+ 	 if (feature) then word sense
+ 	\subsection{LSA -- Past Efforts}
 	\section{Data}
 	\section{Algorithms}
+	 Part of speech tagging and bigram models
+ 	 Use for subset of data that has high predictability
+ 	 Supervised LSA for the rest of the data
+
+ 	 Other methods had low accuracy 
+ 	\subsection{Part-of-Speech}
+ 	\subsection{Semantic Knowledgebase}
+	\subsection{Supervised LSA}
 	\section{Results}

### 2014-05-08 paper.tex
added section for citations
finished transcribing slides. Need to make into nice paper now and ADD CITATIONS

@@
 	  the products of human creativity; works of art collectively 
-	\section{Previous Work}
+	\section{Literature Survey}
 	knowledge based
@@
  	\subsection{LSA -- Past Efforts}
+ 	LSA was one of the first approaches to make use of the co-occurrence model for word meaning.
+The idea, as implemented in the famous 1998 paper by Landauer, is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
+	Then we apply SVD to this matrix. 
+	This approach is essentially unsupervised because it relies on clustering (word co-occurrence matrix) to derive similarities between documents and words.
+
+	Originally, the LSA approach was primarily intended to remove uninformative singular values, and then reconstruct the term-document matrix (Landauer et al 1998).
+The idea there was to compare documents to see how similar they were to each other with noise removed.
+Part of their motivation was to see if co-occurrence representations was in fact how humans represented meaning themselves.
+
+	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
+We do a supervised implementation of this approach.
+
+	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next slide.
+
+	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
+	(this is a latent variable model for co-occurrence data)
+	Model fitting is done with Expectation Maximization (EM).
+
+	-- Non-Negative Matrix Factorization: An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
+	-- minimize Kullback-Leibler divergence instead of Euclidean distance
+
+	-- minimizing Kullback-Leibler divergence is better, since minimizing Euclidean distance makes the normal distribution assumption for language -- language is not Gaussian.
+	-- useful for extraction of semantic dimension 
+	-- turns out to be useful to have no negative relations encoded (all matrix values are positive)
+
+	Van de Cruys (2011): uses this approach on SEMEVAL-2010 dataset.
+The rest of the approach is analogous to SVD-LSA, computing the centroid  of candidate vectors and comparing via Kullback-Leibler divergence to the target vector to determine word sense.
+
 	\section{Data}
+	Senseval-2 (2001) dataset
+	73 words that need to be disambiguated
+	         ex. fine, art, pull, turn, carry
+	Up to 43 senses per word
+	8611 labeled training instances
+	4328 test instances
+
+	brown corpus
+
 	\section{Algorithms}
@@
 	\subsection{Supervised LSA}
+	Our approach uses simple LSA with a supervised learning component.
+
+	1) Build term-document matrix 
+		a) terms are words in Brown Corpus and in training data
+		b) documents are categories of Brown, and concatenated paragraphs of training data with same word sense for ambiguous word
+	2) Apply SVD to get U, D, V^T.
+
+	Supervised part: 
+	3) For each (paragraph, ambiguous word, word_sense) tuple in the training data:
+		a) create vector in the term-document space
+		b) fold this vector into the reduced semantic space of V
+		c) use cosine similarity to come up with the eigentopic most associated with the paragraph. 
+	Then, we have built an association between each word sense and an eigentopic vector in V. 
+	4) For each (paragraph, ambiguous word) in testing data:
+		a) come up with the eigentopic vector associated
+		b) For that eigentopic vector, there is a probability for each word sense for a given word -- we pick the highest probability word sense for the word we are disambiguating
+
+	In other words, for a given eigentopic, we will always pick the same word sense for a given word. This approach has its flaws.
+
+	We also tried a slightly different approach to capture more of the information: For each word, and for each sense of the word, we created a vector by applying cosine similarity to each eigentopic column vector for our training vector (created from paragraph).
+We averaged over all the training data for each word sense.
+Then for testing, we created this vector from the test paragraph and compared via cosine similarity again to determine which word sense was most likely.
+	This approach had issues and we got very bad results. 
+	It might be better in the future to try a modified approach to this (i.e. do something other than average the vectors).
+
 	\section{Results}
+	From Senseval-2:
+
+	Best overall (supervised approach): 64$\%$
+
+	Best unsupervised approach: 40$\%$
+
+	\subsection{POS Bigram Model}
+	POS Bigram Model (w/frequency count > 3)
+
+	Threshold	$80\%	40\%	0\%$
+	Correctly identified	$199	518	574$
+	Total identified	$253	893	1136$
+	$\%$ Accuracy	$78.7\%	58.0\%	50.5\%$
+	$\%$ Coverage	$5.8\%	20.6\%	26.2\%$
+
+	POS Bigram Model (w/frequency count > 0)
+
+	Threshold	$80\%	40\%	0\%$
+	Correctly identified	$466	808	850$
+	Total identified	$898	1641	1826$
+	$\%$ Accuracy	$51.9\%	49.2\%	46.5\%$
+	$\%$ Coverage	$20.7\%	38.7\%	42.2\%$
+
+	Correctly disambiguates:
+	"Marketing too, in its strictest sense, is outside our remit. " (the way in which a word or expression or situation can be interpreted)
+
+	"Before he lost his money he had the good sense to commission John Soane to design the Campden Hill Square house." (a general conscious awareness)
+
+	Supervised LSA: 
+	a) With only the Brown Corpus categories as column vectors ($15$ column vectors -> reduced to $9$) in the term-document matrix: ~ $42\%$
+	b) With the Brown Corpus categories + the word-sense categories (in total, 861 column vectors -> reduced to $140$ column vectors after SVD): ~ $38\%$
+	-- highly dependent on the training data -- different results for different words, some words had lower percentages, some had higher percentages (as low as $7\%$, as high as $61\%$)
+	-- easier to do ambiguous words with fewer senses
+
 	\section{Conclusions}
+	One issue with the LSA approach may be that the corpuses we use (namely, for a given word and a given sense, all the training paragraphs concatenated together) may actually cover a very broad array of topics, and thus a lot of noise might be added.
+While this should theoretically be removed by SVD, it might just be that the 'paragraph topics' were too disjoint and the correlation for different very fine-tuned usage is not strong enough.
+	Examples of failures:
+
+	for the word "fine":
+
+	our program: "elegant"  actual: "thin (in thickness)"
+	our program: "superlative" actual: "elegant"
+
+	and so on... it makes sense that both senses could apply to some of the testing data
+
+	Labeled training data sparsity is a large issue
+
+	Some statistical methods fall short of disambiguating subtle nuances between word senses
+
+	The LSA approach is primarily topic categorization -- we need to use better documents that are more tailored to WSD, perhaps.
+
+	It is hard to use a topic-categorization approach to do fine-tuned WSD.
+
 	\section{Future Work}
+	Could try different document columns for Supervised LSA.
+	Could try applying supervised approach to PLSA or NNMF-LSA.
+
+	Recall Socher et al. (2012) -- Recursive Neural Nets on sentiment trees
+	Integrate with Socher's work on sentiment analysis
+	Found that Socher doesn't disambiguate across certain words such as "mean", "like"
+	Could improve accuracy of sentiment analysis
+
+	Can be applied to translation if WSD is made better
+
+	\section{Citations}
+
+	Need to get list of papers and cite them in text as well. These are on the Google Doc and also in Kiran's Chrome tabs.
 

### 2014-05-08 paper.tex
finished transcibing slides. still need to write actual paper stuff and add citations

@@
 		b) documents are categories of Brown, and concatenated paragraphs of training data with same word sense for ambiguous word
-	2) Apply SVD to get U, D, V^T.
+	2) Apply SVD to get $U$, $D$, $V^T$.
 
 	Supervised part: 
-	3) For each (paragraph, ambiguous word, word_sense) tuple in the training data:
+	3) For each (paragraph, ambiguous word, word sense) tuple in the training data:
 		a) create vector in the term-document space
@@
 
-	Need to get list of papers and cite them in text as well. These are on the Google Doc and also in Kiran's Chrome tabs.
+	Need to get list of papers and cite them in text as well. These are on the Google Doc and also in Kiran's Chrome tabs. Also we all have the book Albert sent out.
 

### 2014-05-11 paper.tex
updated paper again
added a table example

@@
 	\subsection{POS Bigram Model}
+
+	Table Example: 
+    \begin{tabular} {l | c}
+	 \hline
+		Logical Formula & Program Type \\ \hline
+		Implication & Function type $A \rightarrow B$\\ Proof of: & Function \\ \hline
+		Conjunction & Pair type $A * B$ \\ Proof of: &  $(e_1, e_2)$ \\ \hline
+		True & Unit \\ Proof of: &  $()$ \\ \hline
+		False & Void \\ Proof of: & abort, failwith \\ \hline
+		Disjunction & sumtype \\ Proof of: & tagged value \\ \hline
+	 \end{tabular}
+
 	POS Bigram Model (w/frequency count > 3)
@@
 
+	Maybe could apply SVM to the (word sense: cosine-vector) approach (i.e. train an SVM 
+	for every ambiguous word in the training data with the cosine vectors as input)
+
 	\section{Citations}

### 2014-05-11 paper.tex
Update tables

--- 2014-05-08 paper.tex
@@
 	\subsection{POS Bigram Model}
-	POS Bigram Model (w/frequency count > 3)
 
-	Threshold	$80\%	40\%	0\%$
-	Correctly identified	$199	518	574$
-	Total identified	$253	893	1136$
-	$\%$ Accuracy	$78.7\%	58.0\%	50.5\%$
-	$\%$ Coverage	$5.8\%	20.6\%	26.2\%$
-
-	POS Bigram Model (w/frequency count > 0)
-
-	Threshold	$80\%	40\%	0\%$
-	Correctly identified	$466	808	850$
-	Total identified	$898	1641	1826$
-	$\%$ Accuracy	$51.9\%	49.2\%	46.5\%$
-	$\%$ Coverage	$20.7\%	38.7\%	42.2\%$
+	POS Bigram Model (w/frequency count $>$ 3): 
+	\begin{table}[h]
+	\begin{tabular}{|l|l|l|l|}
+	\hline
+	Threshold            & 80\%   & 40\%   & 0\%    \\ \hline
+	Correctly identified & 199    & 518    & 574    \\ \hline
+	Total identified     & 253    & 893    & 1136   \\ \hline
+	\% Accuracy          & 78.7\% & 58.0\% & 50.5\% \\ \hline
+	\% Coverage			 & 5.8\%  & 20.6\% & 26.2\% \\ \hline
+	\end{tabular}
+	\end{table}\\
+	POS Bigram Model (w/frequency count $>$ 0)
+	\begin{table}[h]
+	\begin{tabular}{|l|l|l|l|}
+	\hline
+	Threshold            & 80\%   & 40\%   & 0\%    \\ \hline
+	Correctly identified & 466    & 808    & 850    \\ \hline
+	Total identified     & 898    & 1641   & 1826   \\ \hline
+	\% Accuracy          & 51.9\% & 49.2\% & 46.5\% \\ \hline
+	\% Coverage          & 20.7\% & 38.7\% & 42.2\% \\ \hline
+	\end{tabular}
+	\end{table}
 

### 2014-05-11 paper.tex
some added citations

--- 2014-05-11 paper.tex
@@
 
-	Need to get list of papers and cite them in text as well. These are on the Google Doc and also in Kiran's Chrome tabs. Also we all have the book Albert sent out.
+	1. Agirre, Eneko, and Philip Glenny. Edmonds. Word Sense Disambiguation: Algorithms and Applications. Dordrecht: Springer, 2006. Print.
+
+	2. Phil Katz and Paul Goldsmith-Pinkham. 2006. Word Sense Disambiguation Using Latent Semantic Analysis. 
+	   Retrieved from http://www.sccs.swarthmore.edu/users/07 /pkatz1/cs65f06-final.pdf.
+
+	3. T.K. Landauer, Foltz P.W., and D. Laham. 1998. Introduction to latent semantic analysis. $\textit{Discourse Processes}$, $25:259-284$.
 

### 2014-05-11 paper.tex
updated citations

@@
 	\section{Citations} 
+	.
 
@@
 
-	2. Phil Katz and Paul Goldsmith-Pinkham. 2006. Word Sense Disambiguation Using Latent Semantic Analysis. 
-	   Retrieved from http://www.sccs.swarthmore.edu/users/07 /pkatz1/cs65f06-final.pdf.
+	2. Phil Katz and Paul Goldsmith-Pinkham. 2006. Word Sense Disambiguation Using Latent Semantic Analysis Retrieved from http://www.sccs.swarthmore.edu/users/07 /pkatz1/cs65f06-final.pdf.
 
@@
 
+	4. Thomas Hofmann. 1999. Probabilistic Latent Semantic Analysis. Retrieved from http://cs.brown.edu/~th/papers/Hofmann-UAI99.pdf.
+
+	5. Tim Van de Cruys and Marianna Apidianaki. 2011. Latent Semantic Word Sense Induction and Disambiguation. Retrieved from http://aclweb.org/anthology//P/P11/P11-1148.pdf.
+
+	6. Kirk Baker. 2013. Singular Value Decomposition Tutorial. Retrieved from http://www.ling.ohio-state. edu/~kbaker/pubs/Singular$\_$Value$\_$Decomposition$\_$Tutorial.pdf.
+
 \end{document}

### 2014-05-11 paper.tex
updated citations

@@
 	\section{Algorithms}
-	 Part of speech tagging and bigram models
- 	 Use for subset of data that has high predictability
- 	 Supervised LSA for the rest of the data
+	 Our approach was essentially a pipeline of different sorts of models. 
+	 The first stage consisted of part-of-speech tagging and bigram models, which
+	 was used for the subset of data that had high predictability. 
+	 Originally, we implemented a step that included knowledge-base approaches like
+	 semantic similarity, but later discarded it from the pipeline because its accuracy
+	 was not very good.
 
- 	 Other methods had low accuracy 
+	 For the rest of the data, we implemented a Supervised LSA approach, which was to
+	 an extent a novel approach.
+
+	 We detail the methods in the following sections. 
  	\subsection{Part-of-Speech}

### 2014-05-11 paper.tex
added more detail on supervised LSA

@@
 
-	1) Build term-document matrix 
-		a) terms are words in Brown Corpus and in training data
-		b) documents are categories of Brown, and concatenated paragraphs of training data with same word sense for ambiguous word
-	2) Apply SVD to get $U$, $D$, $V^T$.
+	The steps are as follows:
 
-	Supervised part: 
-	3) For each (paragraph, ambiguous word, word sense) tuple in the training data:
-		a) create vector in the term-document space
-		b) fold this vector into the reduced semantic space of V
-		c) use cosine similarity to come up with the eigentopic most associated with the paragraph. 
+	\begin{enumerate}
+
+	\item Build term-document matrix 
+		\begin{enumerate}
+		\item terms are words in Brown Corpus and in training data
+		\item documents are categories of Brown, and concatenated paragraphs of training data with same word sense for ambiguous word
+		\end{enumerate}
+	\item Apply SVD to get $U$, $D$, $V^T$.
+
+	Then we have the supervised aspect of the LSA.  
+	\item For each (paragraph, ambiguous word, word sense) tuple in the training data:
+		\begin{enumerate}
+		\item create vector in the term-document space
+		\item fold this vector into the reduced semantic space of V
+		\item use cosine similarity to come up with the eigentopic most associated with the paragraph.
+		\end{enumerate} 
 	Then, we have built an association between each word sense and an eigentopic vector in V. 
-	4) For each (paragraph, ambiguous word) in testing data:
-		a) come up with the eigentopic vector associated
-		b) For that eigentopic vector, there is a probability for each word sense for a given word -- we pick the highest probability word sense for the word we are disambiguating
+	\item For each (paragraph, ambiguous word) in testing data:
+		\begin{enumerate}
+		\item come up with the eigentopic vector associated
+		\item For that eigentopic vector, there is a probability for each word sense for a given word -- we pick the highest probability word sense for the word we are disambiguating
+		\end{enumerate}
+
+	\end{enumerate}
 

### 2014-05-11 paper.tex
fixed a subsection heading

@@
 
-	Supervised LSA: 
+	\subsection{Supervised LSA}
+
 	a) With only the Brown Corpus categories as column vectors ($15$ column vectors -> reduced to $9$) in the term-document matrix: ~ $42\%$

### 2014-05-11 paper.tex
updated sections again

@@
 
-	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next slide.
+	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the following sections.
 
-	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
+	\subsubsection{Probabilistic LSA}
+
+	-- Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
 	(this is a latent variable model for co-occurrence data)
@@
 
-	-- Non-Negative Matrix Factorization: An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
+	\subsubsection{Non-Negative Matrix Factorization}
+	-- An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
 	-- minimize Kullback-Leibler divergence instead of Euclidean distance

### 2014-05-11 paper.tex
added more citations

@@
  	LSA was one of the first approaches to make use of the co-occurrence model for word meaning.
-The idea, as implemented in the famous 1998 paper by Landauer, is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
+The idea, as implemented in the famous 1998 paper by Landauer [CITATION], is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
 	Then we apply SVD to this matrix. 
@@
 
-	Originally, the LSA approach was primarily intended to remove uninformative singular values, and then reconstruct the term-document matrix (Landauer et al 1998).
+	Originally, the LSA approach was primarily intended to remove uninformative singular values, and then reconstruct the term-document matrix (Landauer et al 1998) [CITATION].
 The idea there was to compare documents to see how similar they were to each other with noise removed.
@@
 
-	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
+	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering [CITATION].
 We do a supervised implementation of this approach.
@@
 	(this is a latent variable model for co-occurrence data)
-	Model fitting is done with Expectation Maximization (EM).
+	Model fitting is done with Expectation Maximization (EM). [CITATION]
 
 	\subsubsection{Non-Negative Matrix Factorization}
-	-- An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
+	-- An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000) [CITATION].  Van de Cruys (2011) makes use of this technique [CITATION]:
 	-- minimize Kullback-Leibler divergence instead of Euclidean distance
@@
 	\section{Data}
-	Senseval-2 (2001) dataset
+	Senseval-2 (2001) dataset [CITATION]
 	73 words that need to be disambiguated
@@
 
+	7. Bird, Steven, Edward Loper and Ewan Klein (2009), Natural Language Processing with Python. O’Reilly Media Inc.
+
+	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. <http://wordnet.princeton.edu>
+
+	9. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
+
 \end{document}

### 2014-05-11 paper.tex

@@
 	\subsection{Problem Statement}
-	  Multiple word senses
-
-	  ex. bank: "financial institution" or "river bank" or "count on something happening" or "supply/stock held in supply for future use" ...
-
-	  Wrong sense can drastically alter meaning
-
-	  Objective: given context, determine which sense of the word is intended
-
-	  First proposed by Weaver in 1949 as computational task in the early days of MT
-
-	  One of the oldest open problems in computational linguistics
-
-	  AI-Complete Problem
-
-	  Example
-
-	  "Paintings, drawings and sculpture from every period of art during the last 350 years will be on display ranging from a Tudor portrait to contemporary British art."
-	  vs.
-	  "Through casual meetings at cafe's, the artists drew together to form a movement in protest against the waste of war, against nationalism and against everything pompous, conventional or boring in the art of the Western world."
-
-	  the creation of beautiful or significant things 
-      vs. 
-	  the products of human creativity; works of art collectively 
+	Word sense disambiguation is the process of identifying the meaning of a word in its context when an individual word may take on many meanings.
+	It remains one of the oldest open problems in computational lingusitics and is widely considered to be AI-Complete, 
+	or as hard as the problem of making computers as intelligent as people.$^1$ Being able to accurately disambiguate word senses would greatly
+	assist Machine Translation, semantic analysis, and would have significant impact in computational linguistics. However, fine-grained senses
+	in which a word has multiple closely related meanings remains one of the largest challenges in word sense disambiguation. Consider the following
+	example of disambiguating the sense of the word {\emph {art}} from the Senseval-2 competition held in 2001:
+	\begin{enumerate}
+	\item "Paintings, drawings and sculpture from every period of {\emph {art}} during the last 350 years will be on display ranging from a Tudor portrait to contemporary British art."
+	\item "Through casual meetings at cafe's, the artists drew together to form a movement in protest against the waste of war, against nationalism and against everything pompous, conventional or boring in the {\emph {art}} of the Western world."
+	\end{enumerate}
+	In the first example, {\emph {art}} refers to {\emph {the creation of beautiful or significant things}} whereas in the second example, it refers to {\emph {the products of human creativity; works of art collectively}}.
+Such subtle distinctions are part of what makes word sense disambiguation a challenging problem that remains open to this day.
 	\section{Literature Survey}

### 2014-05-11 paper.tex
added more citations

@@
 	Word sense disambiguation is the process of identifying the meaning of a word in its context when an individual word may take on many meanings.
-	It remains one of the oldest open problems in computational lingusitics and is widely considered to be AI-Complete, 
-	or as hard as the problem of making computers as intelligent as people.$^1$ Being able to accurately disambiguate word senses would greatly
+	It remains one of the oldest open problems in computational linguistics and is widely considered to be AI-Complete, 
+	or as hard as the problem of making computers as intelligent as people.$^1$ [CITATION] Being able to accurately disambiguate word senses would greatly
 	assist Machine Translation, semantic analysis, and would have significant impact in computational linguistics. However, fine-grained senses

### 2014-05-11 paper.tex
added section for Code
paper updates
added citation navigli
fixed citation
Merge

--- 2014-05-11 paper.tex
@@
  	LSA was one of the first approaches to make use of the co-occurrence model for word meaning.
-The idea, as implemented in the famous 1998 paper by Landauer [CITATION], is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
+The idea, as implemented in the famous 1998 paper by Landauer, is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
 	Then we apply SVD to this matrix. 
@@
 
-	Originally, the LSA approach was primarily intended to remove uninformative singular values, and then reconstruct the term-document matrix (Landauer et al 1998) [CITATION].
+	Originally, the LSA approach was primarily intended to remove uninformative singular values, and then reconstruct the term-document matrix (Landauer et al 1998).
 The idea there was to compare documents to see how similar they were to each other with noise removed.
@@
 
-	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering [CITATION].
+	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
 We do a supervised implementation of this approach.
 
-	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the following sections.
+	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next slide.
 
-	\subsubsection{Probabilistic LSA}
+	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
+	(this is a latent variable model for co-occurrence data)
+	Model fitting is done with Expectation Maximization (EM).
 
-	-- Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
-	(this is a latent variable model for co-occurrence data)
-	Model fitting is done with Expectation Maximization (EM). [CITATION]
-
-	\subsubsection{Non-Negative Matrix Factorization}
-	-- An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000) [CITATION].  Van de Cruys (2011) makes use of this technique [CITATION]:
+	-- Non-Negative Matrix Factorization: An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
 	-- minimize Kullback-Leibler divergence instead of Euclidean distance
@@
 	\section{Data}
-	Senseval-2 (2001) dataset [CITATION]
+	Senseval-2 (2001) dataset
 	73 words that need to be disambiguated
@@
 	\section{Algorithms}
-	 Our approach was essentially a pipeline of different sorts of models. 
-	 The first stage consisted of part-of-speech tagging and bigram models, which
-	 was used for the subset of data that had high predictability. 
-	 Originally, we implemented a step that included knowledge-base approaches like
-	 semantic similarity, but later discarded it from the pipeline because its accuracy
-	 was not very good.
+	 Part of speech tagging and bigram models
+ 	 Use for subset of data that has high predictability
+ 	 Supervised LSA for the rest of the data
 
-	 For the rest of the data, we implemented a Supervised LSA approach, which was to
-	 an extent a novel approach.
-
-	 We detail the methods in the following sections. 
+ 	 Other methods had low accuracy 
  	\subsection{Part-of-Speech}
@@
 
-	The steps are as follows:
+	1) Build term-document matrix 
+		a) terms are words in Brown Corpus and in training data
+		b) documents are categories of Brown, and concatenated paragraphs of training data with same word sense for ambiguous word
+	2) Apply SVD to get $U$, $D$, $V^T$.
 
-	\begin{enumerate}
-
-	\item Build term-document matrix 
-		\begin{enumerate}
-		\item terms are words in Brown Corpus and in training data
-		\item documents are categories of Brown, and concatenated paragraphs of training data with same word sense for ambiguous word
-		\end{enumerate}
-	\item Apply SVD to get $U$, $D$, $V^T$.
-
-	Then we have the supervised aspect of the LSA.  
-	\item For each (paragraph, ambiguous word, word sense) tuple in the training data:
-		\begin{enumerate}
-		\item create vector in the term-document space
-		\item fold this vector into the reduced semantic space of V
-		\item use cosine similarity to come up with the eigentopic most associated with the paragraph.
-		\end{enumerate} 
+	Supervised part: 
+	3) For each (paragraph, ambiguous word, word sense) tuple in the training data:
+		a) create vector in the term-document space
+		b) fold this vector into the reduced semantic space of V
+		c) use cosine similarity to come up with the eigentopic most associated with the paragraph. 
 	Then, we have built an association between each word sense and an eigentopic vector in V. 
-	\item For each (paragraph, ambiguous word) in testing data:
-		\begin{enumerate}
-		\item come up with the eigentopic vector associated
-		\item For that eigentopic vector, there is a probability for each word sense for a given word -- we pick the highest probability word sense for the word we are disambiguating
-		\end{enumerate}
-
-	\end{enumerate}
+	4) For each (paragraph, ambiguous word) in testing data:
+		a) come up with the eigentopic vector associated
+		b) For that eigentopic vector, there is a probability for each word sense for a given word -- we pick the highest probability word sense for the word we are disambiguating
 
@@
 
-	\subsection{Supervised LSA}
-
+	Supervised LSA: 
 	a) With only the Brown Corpus categories as column vectors ($15$ column vectors -> reduced to $9$) in the term-document matrix: ~ $42\%$
@@
 
-	7. Bird, Steven, Edward Loper and Ewan Klein (2009), Natural Language Processing with Python. O’Reilly Media Inc.
-
-	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. <http://wordnet.princeton.edu>
-
-	9. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
-
 \end{document}

### 2014-05-11 paper.tex
knowledge-based

--- 2014-05-11 paper.tex
@@
  	\subsection{Semantic Knowledgebase}
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
+        Lesk
+        Semantic similarity
 	\subsection{Supervised LSA}
@@
 
-	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. <http://wordnet.princeton.edu>
+	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. http://wordnet.princeton.edu.
 
@@
 
+	10. R. Navigli. Word Sense Disambiguation: a Survey. ACM Computing Surveys, 41(2), ACM Press, 2009, pp. 1-69. [A complete State of the Art in Word Sense Disambiguation]
+
+	\section{Code}
+
+	The code we used in this paper is available at https://github.com/alee101/wsd.
+
 \end{document}

### 2014-05-11 paper.tex

--- 2014-05-11 paper.tex
@@
 
+	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. http://wordnet.princeton.edu.
+
+	10. R. Navigli. Word Sense Disambiguation: a Survey. ACM Computing Surveys, 41(2), ACM Press, 2009, pp. 1-69. [A complete State of the Art in Word Sense Disambiguation]
+
+	\section{Code}
+
+	The code we used in this paper is available at https://github.com/alee101/wsd.
+
 \end{document}

### 2014-05-11 paper.tex
knowledge-based
added sections on PLSA and NNMF

--- 2014-05-11 paper.tex
@@
 
-	-- Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
-	(this is a latent variable model for co-occurrence data)
-	Model fitting is done with Expectation Maximization (EM). [CITATION]
+	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model.
+It uses a probabilistic model known as an aspect model, which is a latent variable model for co-occurrence data.
+It introduces a conditional dependence assumption, namely that the document random variable and the word random variable are independent conditioned on the state of the associated latent variable.
+
+	The Expectation Maximization (EM) algorithm is used for maximum likelihood estimation, as is standard procedure for latent variable models.
+This paper also introduces the notion of continuous latent space, produced by smoothing the discrete distribution due to the representation as a multinomial distribution
+	consisting of a convex combination of factors. This also results in dimension reduction, and we end up with a probablistic latent semantic space.
+
+	The crucial difference between this approach and standard LSA is that LSA, the objective function to determine the optimal decomposition is results from the $L_2$ or Frobenius norm, which brings along with it an internal assumption of Gaussian noise.
+The PLSA model intends to maximize the predictive power of the model instead, which is related to minimizing cross-entropy, or Kullback-Leibler divergence.
+
+	LSA does not define a properly normalized probability distribution, and this is one of its weaknesses.
 
 	\subsubsection{Non-Negative Matrix Factorization}
-	-- An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000) [CITATION].  Van de Cruys (2011) makes use of this technique [CITATION]:
-	-- minimize Kullback-Leibler divergence instead of Euclidean distance
+	Another alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000). 
+	The primary advantages of this approach again relate to minimizing the Kullback-Leibler divergence instead of Euclidean distance. 
+	Again, minimizing Kullback-Leibler divergence is better since minimizing Euclidean distance makes the normal distribution assumption for language -- and language is not Gaussian.
+	It is also useful for extraction of semantic dimension since it turns out to have no negative relations encoded (all matrix values are positive).
 
-	-- minimizing Kullback-Leibler divergence is better, since minimizing Euclidean distance makes the normal distribution assumption for language -- language is not Gaussian.
-	-- useful for extraction of semantic dimension 
-	-- turns out to be useful to have no negative relations encoded (all matrix values are positive)
-
-	Van de Cruys (2011): uses this approach on SEMEVAL-2010 dataset.
+	Van de Cruys et al (2011) [CITATION] applies this approach to the SEMEVAL-2010 dataset.
 The rest of the approach is analogous to SVD-LSA, computing the centroid  of candidate vectors and comparing via Kullback-Leibler divergence to the target vector to determine word sense.
@@
  	\subsection{Semantic Knowledgebase}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
         Lesk

### 2014-05-11 paper.tex
knowledge-based

--- 2014-05-11 paper.tex
@@
         We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
-        Lesk
-        Semantic similarity
+        We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
+We also tried variations that involved including the dictionary definitions of homonyms to try to improve our accuracy, but it didn't change our results very much.
+        We also semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm: https://github.com/alvations/pywsd  We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.
+However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.
 	\subsection{Supervised LSA}

### 2014-05-11 paper.tex

--- 2014-05-11 paper.tex
@@
  	\subsection{Semantic Knowledgebase}
-        Lesk
-        Semantic similarity
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
+        We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
+We also tried variations that involved including the dictionary definitions of homonyms to try to improve our accuracy, but it didn't change our results very much.
+        We also semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm: https://github.com/alvations/pywsd  We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.
+However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.
 	\subsection{Supervised LSA}

### 2014-05-11 paper.tex

--- 2014-05-11 paper.tex
@@
 	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
-	(this is a latent variable model for co-occurrence data)
-	Model fitting is done with Expectation Maximization (EM).
+	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model.
+It uses a probabilistic model known as an aspect model, which is a latent variable model for co-occurrence data.
+It introduces a conditional dependence assumption, namely that the document random variable and the word random variable are independent conditioned on the state of the associated latent variable.
 
-	-- Non-Negative Matrix Factorization: An alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000).  Van de Cruys (2011) makes use of this technique:
-	-- minimize Kullback-Leibler divergence instead of Euclidean distance
+	The Expectation Maximization (EM) algorithm is used for maximum likelihood estimation, as is standard procedure for latent variable models.
+This paper also introduces the notion of continuous latent space, produced by smoothing the discrete distribution due to the representation as a multinomial distribution
+	consisting of a convex combination of factors. This also results in dimension reduction, and we end up with a probablistic latent semantic space.
 
-	-- minimizing Kullback-Leibler divergence is better, since minimizing Euclidean distance makes the normal distribution assumption for language -- language is not Gaussian.
-	-- useful for extraction of semantic dimension 
-	-- turns out to be useful to have no negative relations encoded (all matrix values are positive)
+	The crucial difference between this approach and standard LSA is that LSA, the objective function to determine the optimal decomposition is results from the $L_2$ or Frobenius norm, which brings along with it an internal assumption of Gaussian noise.
+The PLSA model intends to maximize the predictive power of the model instead, which is related to minimizing cross-entropy, or Kullback-Leibler divergence.
 
-	Van de Cruys (2011): uses this approach on SEMEVAL-2010 dataset.
+	LSA does not define a properly normalized probability distribution, and this is one of its weaknesses.
+
+	\subsubsection{Non-Negative Matrix Factorization}
+	Another alternative to using SVD is NNMF, which is a matrix factoring technique introduced by Lee and Seung  (2000). 
+	The primary advantages of this approach again relate to minimizing the Kullback-Leibler divergence instead of Euclidean distance. 
+	Again, minimizing Kullback-Leibler divergence is better since minimizing Euclidean distance makes the normal distribution assumption for language -- and language is not Gaussian.
+	It is also useful for extraction of semantic dimension since it turns out to have no negative relations encoded (all matrix values are positive).
+
+	Van de Cruys et al (2011) [CITATION] applies this approach to the SEMEVAL-2010 dataset.
 The rest of the approach is analogous to SVD-LSA, computing the centroid  of candidate vectors and comparing via Kullback-Leibler divergence to the target vector to determine word sense.

### 2014-05-11 paper.tex
fixed some latex

--- 2014-05-11 paper.tex
@@
  	\subsection{Semantic Knowledgebase}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of < $30\%$, so we discarded them from the pipeline.
         We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.

### 2014-05-11 paper.tex
literature
knowledge-based alg

@@
 	\section{Literature Survey}
-	knowledge based
 
-	unsupervised corpus-based
+        The past word sense disambiguation methods fall into three main categories: knowledge-based, unsupervised corpus-based, and supervised corpus-based methods.
 
-	supervised corpus-based
 	\subsection{Knowledge-based}
-	Lesk's algorithm:
-	two words W1 and W2 with multiple word senses
+
+        One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
 	for each sense i in W1
@@
 	      calculate overlap of i and j in dictionary definitions
-	maximize overlap i and j to determine word senses
+	Maximize overlap i and j to determine the respective word senses of W1 and W2.
 	Semantic similarity:

### 2014-05-11 paper.tex

@@
 	Maximize overlap i and j to determine the respective word senses of W1 and W2.
-	Semantic similarity:
-	calculate path between words in wordnet for each word sense with other words in the context
-	minimize total semantic path to select word sense
-	context can vary from one sentence to length of document
+
+        Another knowledge-based algorithm is semantic similarity.
+In order to calculate semantic similarity, calculate path between words in Wordnet for each possible word sense of the ambiguous word with other words in the context.
+To select the correct word sense, minimize the total semantic path.
+The context of the word depends, and can vary from one sentence to the length of the document.
+Generally, only nouns are used to provide context.
 

### 2014-05-11 paper.tex
fixed latex

@@
  	\subsection{Semantic Knowledgebase}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of < $30\%$, so we discarded them from the pipeline.
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
         We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.

### 2014-05-11 paper.tex
cite

--- 2014-05-11 paper.tex
@@
  	\subsection{Part-of-Speech}
- 	\subsection{Semantic Knowledgebase}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of < $30\%$, so we discarded them from the pipeline.
+ 	\subsection{Semantic Knowledge base}
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
         We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
@@
 
+        11. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd
+
 	\section{Code}

### 2014-05-11 paper.tex
formatting

@@
         One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
+
 	for each sense i in W1
+
 	   for each sense j in W2
+
 	      calculate overlap of i and j in dictionary definitions
+
 	Maximize overlap i and j to determine the respective word senses of W1 and W2.
@@
         We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
+
         We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
 We also tried variations that involved including the dictionary definitions of homonyms to try to improve our accuracy, but it didn't change our results very much.
+
         We also semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm: https://github.com/alvations/pywsd  We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.

### 2014-05-11 paper.tex
final adds
Add CBC writeup

--- 2014-05-11 paper.tex
@@
 	\section{Literature Survey}
+	knowledge based
 
-        The past word sense disambiguation methods fall into three main categories: knowledge-based, unsupervised corpus-based, and supervised corpus-based methods.
+	unsupervised corpus-based
 
+	supervised corpus-based
 	\subsection{Knowledge-based}
-
-        One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
+	Lesk's algorithm:
+	two words W1 and W2 with multiple word senses
 	for each sense i in W1
@@
 	calculate overlap of i and j in dictionary definitions
-	Maximize overlap i and j to determine the respective word senses of W1 and W2.
-
-        Another knowledge-based algorithm is semantic similarity.
-In order to calculate semantic similarity, calculate path between words in Wordnet for each possible word sense of the ambiguous word with other words in the context.
-To select the correct word sense, minimize the total semantic path.
-The context of the word depends, and can vary from one sentence to the length of the document.
-Generally, only nouns are used to provide context.
+	maximize overlap i and j to determine word senses
+	Semantic similarity:
+	calculate path between words in wordnet for each word sense with other words in the context
+	minimize total semantic path to select word sense
+	context can vary from one sentence to length of document
 
 	\subsection{Unsupervised Corpus-based}
-	 Token-based discrimination: cluster contexts in which a given target word appears
-	 Cluster 1: The line was occupied. 
-	 The operator came into the line abruptly.
+	One of the challenges with word sense disambiguation is the scarcity of accurately sense-tagged text, which such datasets usually needing
+	to be manually built by humans. Unsupervied approaches to word sense disambiguation attempt to overcome the bottleneck of acquiring sense-tagged
+	text by operating on untagged corpora and clustering based on either context or word. Clustering by Committee (CBC) [CITATION] is an example of
+	such an approach, formulated by Lin and Pantel in 2002, in which given a target word, clusters of similar words will be output. CBC is a
+	three step algorithm starting first with the construction of a co-occurrence matrix containing measures of the similarity between each word,
+	followed by clustering the most similar elements from this co-occrrence matrix using average link clustering to form the committees, with each
+	target word then being assigned to its most similar committee in the final step.
 
-	 Cluster 2: The line was really long and it took forever to be served. 
- 	 I stood in the queue for about 10 minutes
-
- 	 Use parallel corpus across language to infer sense distinctions across the language
-	 Je vais prendre ma propre décision.
-	 vs.
-	 Je vais prendre ma propre voiture.
 	\subsection{Supervised Corpus-based}
@@
 
-	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering [CITATION].
+	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
 We do a supervised implementation of this approach.
 
-	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the following sections.
+	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next slide.
 
-	\subsubsection{Probabilistic LSA}
-
+	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
 	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model.
@@
 	\section{Algorithms}
-	 Our approach was essentially a pipeline of different sorts of models. 
-	 The first stage consisted of part-of-speech tagging and bigram models, which
-	 was used for the subset of data that had high predictability. 
-	 Originally, we implemented a step that included knowledge-base approaches like
-	 semantic similarity, but later discarded it from the pipeline because its accuracy
-	 was not very good.
+	 Part of speech tagging and bigram models
+ 	 Use for subset of data that has high predictability
+ 	 Supervised LSA for the rest of the data
 
-	 For the rest of the data, we implemented a Supervised LSA approach, which was to
-	 an extent a novel approach.
-
-	 We detail the methods in the following sections. 
+ 	 Other methods had low accuracy 
  	\subsection{Part-of-Speech}
  	\subsection{Semantic Knowledgebase}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
         We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
@@
 
-	7. Bird, Steven, Edward Loper and Ewan Klein (2009), Natural Language Processing with Python. O’Reilly Media Inc.
-
 	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. http://wordnet.princeton.edu.
-
-	9. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
 

### 2014-05-11 paper.tex

@@
 	\section{Literature Survey}
-	knowledge based
 
-	unsupervised corpus-based
+        The past word sense disambiguation methods fall into three main categories: knowledge-based, unsupervised corpus-based, and supervised corpus-based methods.
 
-	supervised corpus-based
 	\subsection{Knowledge-based}
-	Lesk's algorithm:
-	two words W1 and W2 with multiple word senses
+
+        One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
+
 	for each sense i in W1
-	for each sense j in W2
-	calculate overlap of i and j in dictionary definitions
-	maximize overlap i and j to determine word senses
-	Semantic similarity:
-	calculate path between words in wordnet for each word sense with other words in the context
-	minimize total semantic path to select word sense
-	context can vary from one sentence to length of document
+
+	\indent for each sense j in W2
+
+	\indent \indent calculate overlap of i and j in dictionary definitions
+
+	Maximize overlap i and j to determine the respective word senses of W1 and W2.
+
+        Another knowledge-based algorithm is semantic similarity.
+In order to calculate semantic similarity, calculate path between words in Wordnet for each possible word sense of the ambiguous word with other words in the context.
+To select the correct word sense, minimize the total semantic path.
+The context of the word depends, and can vary from one sentence to the length of the document.
+Generally, only nouns are used to provide context.
 
@@
  	\subsection{Part-of-Speech}
- 	\subsection{Semantic Knowledgebase}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of <30\%, so we discarded them from the pipeline.
+ 	\subsection{Semantic Knowledge base}
+        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
+
         We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
 We also tried variations that involved including the dictionary definitions of homonyms to try to improve our accuracy, but it didn't change our results very much.
+
         We also semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm: https://github.com/alvations/pywsd  We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.

### 2014-05-11 paper.tex
fixed

@@
 
-	(Katz et al) first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
+	(Katz et al) [CITATION] first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
 We do a supervised implementation of this approach.
 
-	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next slide.
+	It is worth noting that other similar approaches exist in recent years that are probably more powerful (but more difficult to implement). We detail them in the next sections.
 
-	-- Probabilistic LSA: Formulated as early as 1999, this approach is based on mixture decomposition from latent class model. 
+	\subsubsection{Probabilistic LSA}: 
 	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model.

### 2014-05-11 paper.tex
everyone on same page

@@
 
-	\subsubsection{Probabilistic LSA}: 
+	\subsubsection{Probabilistic LSA}
 	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model.
@@
 	\section{Algorithms}
-	 Part of speech tagging and bigram models
- 	 Use for subset of data that has high predictability
- 	 Supervised LSA for the rest of the data
 
- 	 Other methods had low accuracy 
+	 We implemented a pipeline each with a different type of algorithm in order to do 
+	 word sense disambiguation. The first step is a part-of-speech tagging step that uses
+	 bigram models in order to determine what the usual part of speech is in a certain location. 
+	 We use this approach for a subset of data that has high predictability.
+
+	 Previously, we had a step involving semantic knowledge approaches, but this had low accuracy and we discarded it from the pipeline. We still detail the methods below.
+
+ 	 For the rest of the data, we applied supervised LSA, a novel implementation of the simple LSA algorithm with some ideas drawn from more sophisticated LSA approaches.
+
+ 	 We detail them in the following sections.  
  	\subsection{Part-of-Speech}
@@
 
-        11. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd
+    11. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd.
 

### 2014-05-11 paper.tex
spacing

@@
 
-	\indent for each sense j in W2
+	\indent \indent for each sense j in W2
 
-	\indent \indent calculate overlap of i and j in dictionary definitions
+	\indent \indent \indent calculate overlap of i and j in dictionary definitions
 
@@
  	\subsection{Semantic Knowledge base}
-        We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
+        \indent We attempted a couple of methods that were dictionary-based, but they yielded accuracy rates of $ < 30\%$, so we discarded them from the pipeline.
 
-        We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python: https://github.com/alvations/pywsd We used a basic form of Lesk's algorithm that calculated dictionary paths.
+        We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python.
+[CITATIONS] We used a basic form of Lesk's algorithm that calculated dictionary paths.
 We also tried variations that involved including the dictionary definitions of homonyms to try to improve our accuracy, but it didn't change our results very much.
 
-        We also semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm: https://github.com/alvations/pywsd  We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.
+        We also used semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm.
+[CITATION] We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.
 However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.

### 2014-05-11 paper.tex
fixed merge issues

@@
 
-        One widely used knowledge-based algorithm is Lesk's algorithm.  Given that there are two words W1 and W2 with multiple word senses.
+        One widely used knowledge-based algorithm is Lesk's algorithm.  The algorithm is as follows:
+
+        Given that there are two words W1 and W2 with multiple word senses:
 
@@
         Another knowledge-based algorithm is semantic similarity.
-In order to calculate semantic similarity, calculate path between words in Wordnet for each possible word sense of the ambiguous word with other words in the context.
+In order to calculate semantic similarity, calculate the path between words in Wordnet for each possible word sense of the ambiguous word with other words in the context.
 To select the correct word sense, minimize the total semantic path.
-The context of the word depends, and can vary from one sentence to the length of the document.
+The context of the word can vary from one sentence to the length of the document.
 Generally, only nouns are used to provide context.
@@
 
-	 We implemented a pipeline each with a different type of algorithm in order to do 
-	 word sense disambiguation. The first step is a part-of-speech tagging step that uses
-	 bigram models in order to determine what the usual part of speech is in a certain location. 
-	 We use this approach for a subset of data that has high predictability.
+	 Our approach was essentially a pipeline of different sorts of models. 
+	 The first stage consisted of part-of-speech tagging and bigram models, which
+	 was used for the subset of data that had high predictability. 
+	 Originally, we implemented a step that included knowledge-base approaches like
+	 semantic similarity, but later discarded it from the pipeline because its accuracy
+	 was not very good.
 
-	 Previously, we had a step involving semantic knowledge approaches, but this had low accuracy and we discarded it from the pipeline. We still detail the methods below.
+	 For the rest of the data, we implemented a Supervised LSA approach, which was to
+	 an extent a novel approach.
 
- 	 For the rest of the data, we applied supervised LSA, a novel implementation of the simple LSA algorithm with some ideas drawn from more sophisticated LSA approaches.
-
- 	 We detail them in the following sections.  
+	 We detail the methods in the following sections.  
  	\subsection{Part-of-Speech}
@@
 	It might be better in the future to try a modified approach to this (i.e. do something other than average the vectors).
-
 	\section{Results}
@@
 
-	Supervised LSA: 
-	a) With only the Brown Corpus categories as column vectors ($15$ column vectors -> reduced to $9$) in the term-document matrix: ~ $42\%$
-	b) With the Brown Corpus categories + the word-sense categories (in total, 861 column vectors -> reduced to $140$ column vectors after SVD): ~ $38\%$
+	\subsection{Supervised LSA}
+
+	a) With only the Brown Corpus categories as column vectors ($15$ column vectors $\rightarrow$ reduced to $9$) in the term-document matrix: $ ~ 42\%$
+	b) With the Brown Corpus categories + the word-sense categories (in total, 861 column vectors $\rightarrow$ reduced to $140$ column vectors after SVD): $ ~ 38\%$
 	-- highly dependent on the training data -- different results for different words, some words had lower percentages, some had higher percentages (as low as $7\%$, as high as $61\%$)

### 2014-05-11 paper.tex
updated paper

@@
  	\subsection{Part-of-Speech}
+ 	We constructed two POS bigram models to try and perform coarse-filtering on the data by identifying the senses we could predict with high probability using a part-of-speech model before propogating the data instances further down the pipeline.
+We constructed one bigram model consisting of the POS bigrams containing the word coming before the target word and the target word, and another bigram model consisting of the POS bigrams containing the target word and word following the target word.
+The POS tags were generated by running NLTK's POS-tagger on the sentence containing the target word in each of our training data instances.
+On an input test instance, we would tag the sentence of interest, extract the two bigrams containing the target word, check if either bigram could be found in either of our bigram models, and output a predicted sense key if our predicted probability of the sense key given that bigram exceeded 80\%.
+To avoid skewed probabilities from having only one training data instance with that bigram, but also to ensure sufficient coverage for the already sparse data set, we also set a frequency count threshold of three such that we would only output our predicted sense key if we had seen more than three instances of this particular bigram in our training data and we predicted a probability of over 80\%.
  	\subsection{Semantic Knowledge base}
@@
 However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.
+
+        We also tried Naive Bayes approach using two bigram models similar to the method used for our part of speech models, with one bigram model for bigrams including the word before the target word and the target word, and another bigram model for the target word and the word after the target word.
+This too had a low accuracy rate so we did not include it in our pipeline.
 	\subsection{Supervised LSA}
@@
 
+    9. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
+
 	10. R. Navigli. Word Sense Disambiguation: a Survey. ACM Computing Surveys, 41(2), ACM Press, 2009, pp. 1-69. [A complete State of the Art in Word Sense Disambiguation]

### 2014-05-13 paper.tex
completed paper

@@
 	It remains one of the oldest open problems in computational linguistics and is widely considered to be AI-Complete, 
-	or as hard as the problem of making computers as intelligent as people.$^1$ [CITATION] Being able to accurately disambiguate word senses would greatly
+	or as hard as the problem of making computers as intelligent as people [2]. Being able to accurately disambiguate word senses would greatly
 	assist Machine Translation, semantic analysis, and would have significant impact in computational linguistics. However, fine-grained senses
 	in which a word has multiple closely related meanings remains one of the largest challenges in word sense disambiguation. Consider the following
-	example of disambiguating the sense of the word {\emph {art}} from the Senseval-2 competition held in 2001:
+	example of disambiguating the sense of the word {\emph {art}} from the Senseval-2 competition held in 2001 [1]:
 	\begin{enumerate}
@@
 
-        The past word sense disambiguation methods fall into three main categories: knowledge-based, unsupervised corpus-based, and supervised corpus-based methods.
+        The past word sense disambiguation methods fall into three main categories: knowledge-based, unsupervised corpus-based, and supervised corpus-based methods [9].
 
@@
 
-        One widely used knowledge-based algorithm is Lesk's algorithm.  The algorithm is as follows:
+        One widely used knowledge-based algorithm is Lesk's algorithm [2].  The algorithm is as follows:
 
@@
 	to be manually built by humans. Unsupervied approaches to word sense disambiguation attempt to overcome the bottleneck of acquiring sense-tagged
-	text by operating on untagged corpora and clustering based on either context or word. Clustering by Committee (CBC) [CITATION] is an example of
-	such an approach, formulated by Lin and Pantel in 2002, in which given a target word, clusters of similar words will be output. CBC is a
+	text by operating on untagged corpora and clustering based on either context or word. Clustering by Committee (CBC) is an example of
+	such an approach, formulated by Lin and Pantel in 2002 [2], in which given a target word, clusters of similar words will be output. CBC is a
 	three step algorithm starting first with the construction of a co-occurrence matrix containing measures of the similarity between each word,
@@
 	\subsection{Supervised Corpus-based}
-	 Use annotated corpus to build model
- 	 ex. to know: 1) be aware of piece of information
-                              I want to know who is winning.
-                              I know that the president lied.
-                             2) know person
+	 The supervised corpus-based methods use an annotated corpus to build a model, and makes predictions on previous word senses based on this model.
+For example, for the definition to know, it could mean:
+
+ 	1) be aware of piece of information
+
+    Usages: I want to know who is winning.  I know that the president lied.
+
+    2) know a person
+
     She doesn't know the composer.
-                             Do you know my sister?
-	 Use context of how word usually appears (bigram/trigram models)
- 	 if (feature) then word sense
+
+    Usages: Do you know my sister?
+
+    The model uses the context of how a word usually appears and creates bigram/trigram models on surrounding words.  These models are applied to determine word sense in other instances.
+
  	\subsection{LSA -- Past Efforts}
  	LSA was one of the first approaches to make use of the co-occurrence model for word meaning.
-The idea, as implemented in the famous 1998 paper by Landauer, is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
+The idea, as implemented in the famous 1998 paper by Landauer [12], is that given a set of corpuses, we build a term-document matrix where words are on the rows and documents are on the columns, and the frequencies are in the corresponding cells.
 	Then we apply SVD to this matrix. 
@@
 
-	(Katz et al) [CITATION] first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
+	(Katz et al) [6] first applied LSA to WSD in an unsupervised approach by folding new documents with ambiguous word into the semantic space created by the SVD of the term-document matrix, and then used cosine-based clustering.
 We do a supervised implementation of this approach.
@@
 	\subsubsection{Probabilistic LSA}
-	Formulated as early as 1999 in a paper by Hofmann [CITATION], this approach is based on mixture decomposition from latent class model.
+	Formulated as early as 1999 in a paper by Hofmann [10], this approach is based on mixture decomposition from latent class model.
 It uses a probabilistic model known as an aspect model, which is a latent variable model for co-occurrence data.
@@
 
-	Van de Cruys et al (2011) [CITATION] applies this approach to the SEMEVAL-2010 dataset.
+	Van de Cruys et al (2011) [11] applies this approach to the SEMEVAL-2010 dataset.
 The rest of the approach is analogous to SVD-LSA, computing the centroid  of candidate vectors and comparing via Kullback-Leibler divergence to the target vector to determine word sense.
@@
 	\section{Data}
-	Senseval-2 (2001) dataset
-	73 words that need to be disambiguated
-	         ex. fine, art, pull, turn, carry
-	Up to 43 senses per word
-	8611 labeled training instances
-	4328 test instances
-
-	brown corpus
+	We used the Senseval-2 dataset from 2001 [1], which consists of 73 words with multiple senses to be disambiguated.
+In total, there were 8611 training instances labeled with the WordNet sense key of the target word to be disambiguated, and 4328 test instances.
+All the data was provided in XML format.
+After parsing all training instances, we used only the sentence containing each target word for our POS bigram models and some of our dictionary-based methods, but the entire paragraph context for our LSA-based method.
+In addition to Senseval-2 dataset, we used the Brown corpus in our LSA-based method.
 
@@
 We constructed one bigram model consisting of the POS bigrams containing the word coming before the target word and the target word, and another bigram model consisting of the POS bigrams containing the target word and word following the target word.
-The POS tags were generated by running NLTK's POS-tagger on the sentence containing the target word in each of our training data instances.
+The POS tags were generated by running NLTK's POS-tagger [3] on the sentence containing the target word in each of our training data instances.
 On an input test instance, we would tag the sentence of interest, extract the two bigrams containing the target word, check if either bigram could be found in either of our bigram models, and output a predicted sense key if our predicted probability of the sense key given that bigram exceeded 80\%.
@@
 
-        We used Lesk's algorithm on the brown corpus, with an implementation that was based upon a previous implementation in python.
-[CITATIONS] We used a basic form of Lesk's algorithm that calculated dictionary paths.
+        We used Lesk's algorithm on the Brown corpus, with an implementation that was based upon a previous implementation in python.
+[5, 7] We used a basic form of Lesk's algorithm that calculated dictionary paths.
 We also tried variations that involved including the dictionary definitions of homonyms to try to improve our accuracy, but it didn't change our results very much.
@@
         We also used semantic similarity methods on the brown corpus, using an implementation by the same author as Lesk's algorithm.
-[CITATION] We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.
+We tried all three methods: path similarity, Wu-Palmer, and Leacock-Chordorow's algorithm to see if they would yield high accuracy rates.
 However, each method was only accurate for certain words, but none of them could consistently identify the correct word sense.
@@
 		\end{enumerate}
-	\item Apply SVD to get $U$, $D$, $V^T$.
+	\item Apply SVD to get $U$, $D$, $V^T$ [4].
 
@@
 	\section{Results}
-	From Senseval-2:
-
-	Best overall (supervised approach): 64$\%$
-
-	Best unsupervised approach: 40$\%$
+	For comparison, the highest accuracy obtained in the 2001 Senseval-2 competition was $64\%$ using a supervised approach. The best unsupervised approach had an accuracy of $40\%$.
 
@@
 
-	Correctly disambiguates:
+	Here are some examples of phrases that our POS Bigram model correctly disambiguates:
 	"Marketing too, in its strictest sense, is outside our remit. " (the way in which a word or expression or situation can be interpreted)
@@
 
-	a) With only the Brown Corpus categories as column vectors ($15$ column vectors $\rightarrow$ reduced to $9$) in the term-document matrix: $ ~ 42\%$
-	b) With the Brown Corpus categories + the word-sense categories (in total, 861 column vectors $\rightarrow$ reduced to $140$ column vectors after SVD): $ ~ 38\%$
-	-- highly dependent on the training data -- different results for different words, some words had lower percentages, some had higher percentages (as low as $7\%$, as high as $61\%$)
-	-- easier to do ambiguous words with fewer senses
+	We give two results: 
+	with only the Brown Corpus categories as column vectors ($15$ column vectors $\rightarrow$ $9$ column vectors after SVD) in the term-document matrix, the accuracy of word sense disambiguation was $ ~ 42\%$ (average over all the words).
+
+    With the Brown Corpus categories as well as the word-sense categories (in total, 861 column vectors $\rightarrow$ $140$ column vectors after SVD), the accuracy was on average $ ~ 31\%$, though individual accuracies for different words ranged from $7\%$ to $61\%$.
 
 	\section{Conclusions}
+
+	\subsection{Part-of-Speech Tagging}
+
+	Part-of-speech performed typically very well on the subsets of the data that it deemed itself accurate enough to deal with.
+The main issue with POS was the subset of the data on which it was actually accurate enough to take care of.
+If the threshold was set at $80\%$, POS was applied to about only $6\%$of the data.
+Even when the threshold was set at $0\%$, POS only took care of $42.2\%$ of the data, since
+	a large number of the bigram pairs (of part-of-speech relations) never showed up in the dataset. This indicates an issue with sparsity of the data.
+
+	\subsection{Supervised LSA}
 	One issue with the LSA approach may be that the corpuses we use (namely, for a given word and a given sense, all the training paragraphs concatenated together) may actually cover a very broad array of topics, and thus a lot of noise might be added.
 While this should theoretically be removed by SVD, it might just be that the 'paragraph topics' were too disjoint and the correlation for different very fine-tuned usage is not strong enough.
-	Examples of failures:
 
-	for the word "fine":
+	Here are some examples of where our approach fails with Supervised-LSA:
 
-	our program: "elegant"  actual: "thin (in thickness)"
-	our program: "superlative" actual: "elegant"
+	For the word "fine":
 
-	and so on... it makes sense that both senses could apply to some of the testing data
+	Our program: "elegant"
 
-	Labeled training data sparsity is a large issue
+	Actual: "thin (in thickness)"
 
-	Some statistical methods fall short of disambiguating subtle nuances between word senses
+	Our program: "superlative"
 
-	The LSA approach is primarily topic categorization -- we need to use better documents that are more tailored to WSD, perhaps.
+	Actual: "elegant"
 
-	It is hard to use a topic-categorization approach to do fine-tuned WSD.
+	There are a large amount of errors in cases where it would be difficult for a human to disambiguate
+	between the senses because the senses are very finely separated in meaning. Thus our approach falls short of disambiguating subtle nuances between word senses.
+
+	Because the LSA approach is primarily topic categorization, we need to use better documents that are more tailored to WSD.
+
+	Another issue is the sparsity of our labeled training data: because we potentially do not have enough 
+	data for a given word sense, it becomes a lot more difficult to build a valid topic model.
+Thus it may be that we need more outside training data that has a single ambiguous word used in a specific word sense in multiple different ways.
+Another necessary improvement would be the use of this word sense in a constant topic area -- in other words, it would be nice if we had labeled data that used the word "fine" meaning "thin" only in sentences relating to cutting in a fine fashion (as opposed to being intermingled with sentences regarding a "fine figure", where "fine" still means "thin".)
+
+	Again, since the accuracy was highly dependent on training data, it was easier to disambiguate
+	ambiguous words with fewer senses because there were fewer possible ways to categorize the word senses.
+	Also, the length of the document column texts were smaller as a result for the associated word senses.
+
+	Due to the difficulty of gathering enough appropriate data, it is hard to use a topic-categorization approach to do fine-tuned WSD.
 
 	\section{Future Work}
-	Could try different document columns for Supervised LSA.
-	Could try applying supervised approach to PLSA or NNMF-LSA.
 
-	Recall Socher et al. (2012) -- Recursive Neural Nets on sentiment trees
-	Integrate with Socher's work on sentiment analysis
-	Found that Socher doesn't disambiguate across certain words such as "mean", "like"
-	Could improve accuracy of sentiment analysis
+	There are many directions for future work with this project. 
+	Regarding just the LSA-portion of the pipeline, several improvements could be made.
+We could try different document columns for Supervised LSA-- the method's success is in large part due to choosing document-columns appropriately.
+Perhaps it would make sense to create our own corpus and analyze a specific word to get really good accuracy with just disambiguating that word.
+We could also try improving the statistical rigor of the procedure itself by utilizing a supervised approach to PLSA or NNMF-LSA, as described earlier in the paper.
+We could also try an SVM approach with the supervised portion of the word -- build an SVM out of the cosine vectors, and train an SVM to recognize which word sense a cosine vector is most likely to be given a cosine vector for a test data input.
 
-	Can be applied to translation if WSD is made better
-
-	Maybe could apply SVM to the (word sense: cosine-vector) approach (i.e. train an SVM 
-	for every ambiguous word in the training data with the cosine vectors as input)
+	The other approach we can take to extend this paper is applications. 
+	Word-Sense Disambiguation would be relevant to the field of sentiment analysis.
+Socher et al (2013) [8]created a sentiment analysis pipeline with Recursive Neural Tensor Networks (RNTNs).
+However, there is no word-sense disambiguation step, which may affect the accuracy of the process, and words like "mean" and "like" are not disambiguated correctly.
+We could potentially improve the accuracy of sentiment analysis by including a word-sense disambiguation step (perhaps improved from ours) into the pipeline.
 
@@
 
-	1. Agirre, Eneko, and Philip Glenny. Edmonds. Word Sense Disambiguation: Algorithms and Applications. Dordrecht: Springer, 2006. Print.
+    1. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
 
-	2. Phil Katz and Paul Goldsmith-Pinkham. 2006. Word Sense Disambiguation Using Latent Semantic Analysis Retrieved from http://www.sccs.swarthmore.edu/users/07 /pkatz1/cs65f06-final.pdf.
+	2. Agirre, Eneko, and Philip Glenny. Edmonds. Word Sense Disambiguation: Algorithms and Applications. Dordrecht: Springer, 2006. Print.
 
-	3. T.K. Landauer, Foltz P.W., and D. Laham. 1998. Introduction to latent semantic analysis. $\textit{Discourse Processes}$, $25:259-284$.
+	3. Bird, Steven, Edward Loper and Ewan Klein (2009), Natural Language Processing with Python. O’Reilly Media Inc.
 
-	4. Thomas Hofmann. 1999. Probabilistic Latent Semantic Analysis. Retrieved from http://cs.brown.edu/~th/papers/Hofmann-UAI99.pdf.
+	4. Kirk Baker. 2013. Singular Value Decomposition Tutorial. Retrieved from http://www.ling.ohio-state. edu/~kbaker/pubs/Singular$\_$Value$\_$Decomposition$\_$Tutorial.pdf.
 
-	5. Tim Van de Cruys and Marianna Apidianaki. 2011. Latent Semantic Word Sense Induction and Disambiguation. Retrieved from http://aclweb.org/anthology//P/P11/P11-1148.pdf.
+    5. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd.
 
-	6. Kirk Baker. 2013. Singular Value Decomposition Tutorial. Retrieved from http://www.ling.ohio-state. edu/~kbaker/pubs/Singular$\_$Value$\_$Decomposition$\_$Tutorial.pdf.
+	6. Phil Katz and Paul Goldsmith-Pinkham. 2006. Word Sense Disambiguation Using Latent Semantic Analysis Retrieved from http://www.sccs.swarthmore.edu/users/07 /pkatz1/cs65f06-final.pdf.
 
-	8. Princeton University "About WordNet." WordNet. Princeton University. 2010. http://wordnet.princeton.edu.
+	7. Princeton University "About WordNet." WordNet. Princeton University. 2010. http://wordnet.princeton.edu.
 
-    9. ACL-SIGLEX. 2001. Evaluation Exercises for the Semantic Analysis of Text. Retrieved from http://www.senseval.org/.
+    8.
+Richard Socher, Alex Perelygin, et al.
+2013.
+Recursive Deep Models for Semantic Compositionality Over a Sentiment Treebank.
+Retrieved from http://nlp.stanford.edu/$~$socherr/EMNLP2013$\_$RNTN.pdf.
 
-	10. R. Navigli. Word Sense Disambiguation: a Survey. ACM Computing Surveys, 41(2), ACM Press, 2009, pp. 1-69. [A complete State of the Art in Word Sense Disambiguation]
+	9. R. Navigli. Word Sense Disambiguation: a Survey. ACM Computing Surveys, 41(2), ACM Press, 2009, pp. 1-69. [A complete State of the Art in Word Sense Disambiguation]
 
-    11. Liling Tan. 2014. Pywsd: Python Implementations of Word Sense Disambiguation (WSD) Technologies [software]. Retrieved from https://github.com/alvations/pywsd.
+	10. Thomas Hofmann. 1999. Probabilistic Latent Semantic Analysis. Retrieved from http://cs.brown.edu/~th/papers/Hofmann-UAI99.pdf.
+
+	11. Tim Van de Cruys and Marianna Apidianaki. 2011. Latent Semantic Word Sense Induction and Disambiguation. Retrieved from http://aclweb.org/anthology//P/P11/P11-1148.pdf.
+
+	12. T.K. Landauer, Foltz P.W., and D. Laham. 1998. Introduction to latent semantic analysis. $\textit{Discourse Processes}$, $25:259-284$.
 

### 2014-05-14 evaluate.py
final

@@ -12,7 +12,7 @@ with open('out') as f_predictions:
         (word, iid, sensekey) = fields[:3]
         metadata = fields[3:]
         if sensekey in answers[word][iid]:
-            print 'Yes', metadata, sensekey
+            print 'Yes'
         else:
-            print 'No', metadata, sensekey, 'vs.', answers[word][iid]
+            print 'No'
 

### 2014-05-14 wsd.py

@@ -12,48 +12,27 @@ training_dict = dataparser.parse_training_data('data/eng-lex-sample.training.xml
 test_dict = dataparser.parse_test_data('data/eng-lex-sample.evaluation.xml')
 (forward_bigrams_test, back_bigrams_test) = bigram_model.pos_bigram_test_data(test_dict)
 
-# Construct a copy for easier removal of predictions
-# test_instances = defaultdict(lambda: defaultdict(list))
-# for word in test_dict:
-#     for instance in test_dict[word]:
-#         test_instances[word][instance.iid] = instance
+predicted = []
+for word in back_bigrams_test:
+    for bigram in back_bigrams_test[word]:
+        back_prediction = bigram_model.predict_sensekey(back_bigrams, word, bigram)
+        instance_id = back_bigrams_test[word][bigram]
+        if back_prediction:
+            predicted.append(instance_id)
+            print word, instance_id, back_prediction[0], 'back'
 
-# predicted = []
-# for word in back_bigrams_test:
-#     for bigram in back_bigrams_test[word]:
-#         back_prediction = bigram_model.predict_sensekey(back_bigrams, word, bigram)
-#         instance_id = back_bigrams_test[word][bigram]
-#         if back_prediction:
-#             predicted.append(instance_id)
-#             #del test_instances[word][instance_id]
-#             #print word, back_bigrams_test[word][bigram], back_prediction[0], back_prediction[1]
-#             print word, instance_id, back_prediction[0], 'back'
+for word in forward_bigrams_test:
+    for bigram in forward_bigrams_test[word]:
+        forward_prediction = bigram_model.predict_sensekey(forward_bigrams, word, bigram)
+        instance_id = forward_bigrams_test[word][bigram]
+        if forward_prediction and instance_id not in predicted:
+            predicted.append(instance_id)
+            print word, instance_id, forward_prediction[0], 'forward'
 
-# for word in forward_bigrams_test:
-#     for bigram in forward_bigrams_test[word]:
-#         forward_prediction = bigram_model.predict_sensekey(forward_bigrams, word, bigram)
-#         instance_id = forward_bigrams_test[word][bigram]
-#         if forward_prediction and instance_id not in predicted:
-#             predicted.append(instance_id)
-#             #del test_instances[word][instance_id]
-#             # print word, forward_bigrams_test[word][bigram], forward_prediction[0], forward_prediction[1]       
[…]
